### 2013-04-09 exam6/2.tex
problem 2

\begin{problem} \pts{25}
\noindent
Tobin-Hochstadt has been asked to serve on a review panel for the
 National Science Foundation, which requires he read and make notes on
 a set of grant proposals the government is considering to fund.
  Rather than read the proposals he's been assigned, he's decided to
 make a program for modeling his notes.  His notes take the form of an
 outline, which consists of a peice of text and a list of (sub)notes.
  For example, here's one of his notes (thankfully not in his
 handwritting):
\begin{verbatim}
       NSF Proposal 1218390
       |
       +- Overview
       |  |
       |  +- WAT?
       |  |
       |  +- Motivations
       |     |
       |     +- unmotivating
       |
       +- Middle (fell asleep)
       |
       +- Conclusions
       |
       +- Budget
          |
          +- very large
          |
          +- underfund lots of BU undergrads
\end{verbatim}

@@

@@

@@

@@

\begin{solution}
\newpage
\begin{verbatim}
// 2 pt structure (including purpose etc)
class Thunk<X> implements Computation<X> {
    Delay<X> s;
    Thunk(Computation<X> c) {
        this.s = new Frozen<X>(c);
    }
// 1 pts 
    public X run() {
        this.s = this.s.force();
        return this.s.val();
    }
}
\end{verbatim}
\newpage
\begin{verbatim}
// 7 pts for the code in general, may have different design
interface Delay<X> {
    Delay<X> force();
    X val();
}
class Frozen<X> implements Delay<X> {
    Computation<X> c;
    Frozen(Computation<X> c) {
        this.c = c;
    }
    public Delay<X> force() {
        return new Thaw<X>(this.c.run());
    }
    public X val() {
        return null;
    }
}
class Thaw<X> implements Delay<X> {
    X x;
    Thaw(X x) {
        this.x = x;
    }
    public Delay<X> force() {
        return this;
    }
    public X val() {
        return this.x;
    }
}
\end{verbatim}
\newpage
\begin{verbatim}
// 2 pts tests
class Examples {
    void testThunk(Tester t) {
        Computation<Integer> count = new Count();
        t.checkExpect(count.run(), 0);
        t.checkExpect(count.run(), 1);
        t.checkExpect(count.run(), 2);
        t.checkExpect(count.run(), 3);
        Computation<Integer> thunk = new Thunk<Integer>(new Count());
        t.checkExpect(thunk.run(), 0);
        t.checkExpect(thunk.run(), 0);
    }

}
\end{verbatim}
\end{solution}

>>>>

\begin{problem} \pts{25}
\noindent
Tobin-Hochstadt has been asked to serve on a review panel for the
 National Science Foundation, which requires he read and make notes on
 a set of grant proposals the government is considering to fund.
  Rather than read the proposals he's been assigned, he's decided to
 make a program for modeling his notes.  His notes take the form of an
 outline, which consists of a peice of text and a list of (sub)notes.
  For example, here's one of his notes (thankfully not in his
 handwriting):
\begin{verbatim}
       NSF Proposal 1218390
       |
       +- Overview
       |  |
       |  +- WAT?
       |  |
       |  +- Motivations
       |     |
       |     +- unmotivating
       |
       +- Middle (fell asleep)
       |
       +- Conclusions
       |
       +- Budget
          |
          +- very large
          |
          +- underfund lots of BU undergrads
\end{verbatim}

@@

\begin{solution}
\begin{verbatim}
// 5 pts for Note
class Note {
    String txt;
    List<Note> subnotes;

    Note(String txt) {
        this(txt, new Empty<Note>());
    }

    Note(String txt, List<Note> subnotes) {
        this.txt = txt;
        this.subnotes = subnotes;
    }

}

// 4 pts for List
interface List<X> {}

class Empty<X> implements List<X> {
    Empty() {}
}

class Cons<X> implements List<X> {
    X first;
    List<X> rest;

    Cons(X first, List<X> rest) {
        this.first = first;
        this.rest = rest;
    }
}

\end{verbatim}
\end{solution}

@@

\begin{solution}
\begin{verbatim}

//> 4 pts for interface defintions

interface ListVisitor<X,R> {
    R visitEmpty();
    R visitCons(X first, List<X> rest);
}

// in List
    <R> R accept(ListVisitor<X,R> v);

interface NoteVisitor<R> {
    R visitNote(String txt, List<Note> subnotes);
}

//> 4 pts for accept methods
// in Note
    <R> R accept(NoteVisitor<R> v) {
        return v.visitNote(this.txt, this.subnotes);
    }

// in Empty
    public <R> R accept(ListVisitor<X,R> v) {
        return v.visitEmpty();
    }

// in Cons
    public <R> R accept(ListVisitor<X,R> v) {
        return v.visitCons(this.first, this.rest);
    }
\end{verbatim}
\end{solution}

@@

\begin{solution}
\begin{verbatim}
//> 4 pts
// Nesting Depth with recursion
class NestDepthR implements NoteVisitor<Integer> {
    NestDepthR () {}
    public Integer visitNote(String txt, List<Note> subnotes) {
        return 1 + subnotes.accept(new NestDepthListR());
    }
}

//> 4 pts
class NestDepthListR implements ListVisitor<Note,Integer> {
    NestDepthListR () {}
    public Integer visitEmpty() {
        return 0;
    }
    public Integer visitCons(Note first, List<Note> rest) {
        return Math.max(first.accept(new NestDepthR()),
                        rest.accept(this));
    }
}
\end{verbatim}
\end{solution}

@@

\begin{solution}
\newpage
\begin{verbatim}
// 2 pt structure (including purpose etc)
class Thunk<X> implements Computation<X> {
    Delay<X> s;
    Thunk(Computation<X> c) {
        this.s = new Frozen<X>(c);
    }
// 1 pts 
    public X run() {
        this.s = this.s.force();
        return this.s.val();
    }
}
\end{verbatim}
\newpage
\begin{verbatim}
// 7 pts for the code in general, may have different design
interface Delay<X> {
    Delay<X> force();
    X val();
}
class Frozen<X> implements Delay<X> {
    Computation<X> c;
    Frozen(Computation<X> c) {
        this.c = c;
    }
    public Delay<X> force() {
        return new Thaw<X>(this.c.run());
    }
    public X val() {
        return null;
    }
}
class Thaw<X> implements Delay<X> {
    X x;
    Thaw(X x) {
        this.x = x;
    }
    public Delay<X> force() {
        return this;
    }
    public X val() {
        return this.x;
    }
}
\end{verbatim}
\newpage
\begin{verbatim}
// 2 pts tests
class Examples {
    void testThunk(Tester t) {
        Computation<Integer> count = new Count();
        t.checkExpect(count.run(), 0);
        t.checkExpect(count.run(), 1);
        t.checkExpect(count.run(), 2);
        t.checkExpect(count.run(), 3);
        Computation<Integer> thunk = new Thunk<Integer>(new Count());
        t.checkExpect(thunk.run(), 0);
        t.checkExpect(thunk.run(), 0);
    }
}
\end{verbatim}
\end{solution}
